%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experiences}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Computer Science Initiative Department} % Organization
{Research Intern, Brookhaven National Laboratory} % Job title
{Upton, NY} % Location
{May 2017 - Aug. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%\item {Worked on large scale scientific data mining for streaming data.}
\item{Worked on algorithms that power scientific data mining and understanding. Completed several projects including building machine-learned anomaly detection model, improving the data representation tool and introducing new dimensionality reduction model for streaming data.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{GI Translational Research Lab} % Organization
{Research Intern, Center of Excellence in Wireless and Information Technology} % Job title
{Stony Brook, NY} % Location
{Jun. 2014 - Aug. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%\item {Worked on scientific data analysis for heterogeneous biological data. Focused on building models to better understand accounts and media.}
\item{ Worked on building models and novel approaches that can better understand heterogeneous biological data. Responsibilities included retrieving important features, analyzing experiment results and building tools to improve productivity.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Computer Science Department} % Job title
{Teaching Assistant, Stony Brook University} % Organization
{Stony Brook, NY} % Location
{Sep. 2015 - May 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{CSE 130: Introduction to C Programing}
\item{CSE 214: Computer Science II (Java Programming)}
\end{cvitems}
}

%\cventry
%{Applied Mathematics and Statistics Department} % Job title
%{}
%{}
%{Sep. 2012 - May 2013} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%\item{AMS 210: Linear Algebra}
%\end{cvitems}
%}

%------------------------------------------------

\end{cventries}