%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\projentry
{Embedding Representation for Streaming Data} % Name
{Python} % Skills
{ 
\begin{cvitems}
\item{Proposed a one-pass, limited memory streaming classical Multidimensional Scaling ({MDS}) algorithm with higher approximation accuracy. It can be used as a dimension reduction tool to sequentially represent high dimensional data such as text and images, with a speedup of 13X.}
\end{cvitems}
}


%------------------------------------------------

\projentry
{Representation Framework for Document Clustering and Labeling} % Name
{Python, Javascript} % Skills
{ 
\begin{cvitems}
\item{Developed an embedding representation framework for document clustering. Proposed two metrics to semantically allocate unlabeled documents into the corresponding appropriate cluster. Productized as an internal tool for data representation in Brookhaven National Lab KBase project.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Time Series Anomaly Detection for Unusual Status in Data Center} % Name
{C++} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Detect time series anomalies in the performance of streaming measurements among sensors. Propose approaches for the diagnosis of the anomaly status (e.g. overheating) and was adopted by RACF Data Center in Brookhaven National Lab.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Sequence Modeling for Weather Prediction} % Name
{Python} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Implemented Recursive Neural Network ({RNN}) using TensorFlow for weather forecasting, which applied among multivariate time series data collected by sensors, such as temperature, air pressure, humanity etc.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Image Detection for Human Upper Bodies} % Name
{Python} % Skills
{
\begin{cvitems}
\item{Implemented a Support Vector Machine ({SVM}) classifier to detect images with human upper bodies. The classifier is used to distinguish upper-body patches from non-upper-body patches and used Histogram of Oriented Gradient (HOG) algorithm for feature selection.}
\end{cvitems}
}

%------------------------------------------------

%\projentry
%{Rating Prediction Based on Yelp Reviews} % Name
%{Python, Matlab} % Skills
%{ % Description(s) of experience/contributions/knowledge
%\begin{cvitems}
%\item{Implemented a {LASSO} regression solver to predict the number of stars a restaurant will receive based on the text reviews, resulting a 91\% accuracy.}
%\end{cvitems}
%}

%------------------------------------------------

%\projentry
%{Predictive Model for Biological Data Analysis} % Name
%{C++} % Skills
%{ % Description(s) of experience/contributions/knowledge
%\begin{cvitems}
%\item{Developed a LASSO regression solver to predict and improve experimental design. It was integrated into a bioinformatics system that enables the scientist to upload their own data and analyze it in School of Medicine of Stony Brook University.}
%\end{cvitems}
%}

%------------------------------------------------

\projentry
{Novel Load-Balancer Developed for Heterogeneous Clusters} % Name
{C, PHP, Httperf, Apache} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Proposed a scalable Load Balancers for large heterogeneous cluster systems, which provided low response times without incurring significant overhead. Validation experiments performed on both Apache based clusters and Amazon EC2 web service.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Routing Allocation Algorithm Developed for Routing Allocation of CDN Data Centers} % Name
{C, PHP, Httperf, Apache} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Proposed a geographical allocation algorithm for data centers to improve the performance among CDN services, with an approximation ratio no more than 1.65. Validation experiments performed on real web service with Apache based LBs.}
\end{cvitems}
}

%------------------------------------------------

%\projentry
%{Social Networking Website Development} % Name
%{JDBC, MySQL, HTML, JavaScript} % Skills
%{ % Description(s) of experience/contributions/knowledge
%\begin{cvitems}
%\item{Designed a relational database system to support the operations of a social networking website, which contains user-level transactions, user access control and user-friendly interface.}
%\end{cvitems}
%}

%------------------------------------------------
\end{cventries}