%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\projentry
{Streaming Classical Multidimensional Scaling} % Name
{Python} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Proposed a one-pass, limited memory streaming classical Multidimensional Scaling ({MDS}) algorithm with higher approximation accuracy. It can be used as a dimension reduction tool to sequentially represent high dimensional data such as text and images.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Streaming Representation for Online Corpus} % Name
{Python} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Proposed a representation framework for streaming text data. It can be utilized to semantically reconstruct text data and summarize the important information for data understanding over time. Productized as an internal tool for data representation in Brookhaven National Lab KBase project.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Time Series Anomaly Detection for Unusual Status in Data Center} % Name
{Python} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Generated a pattern discovery method using Long Short Term Memory ({LSTM}) for anomaly detection among multivariate time series data. The method was adopted to detect unusual status (e.g. overheating) for RACF Data Center in Brookhaven National Lab.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Sequence Modeling for Weather Prediction} % Name
{Python} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Implemented Recursive Neural Network ({RNN}) using TensorFlow backend for weather forecasting, which applied among multivariate time series data collected by sensors, such as temperature, air pressure, humanity etc.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Image Detection for Human Upper Bodies} % Name
{Python} % Skills
{
\begin{cvitems}
\item{Implemented a Support Vector Machine ({SVM}) classifier to detect images with human upper bodies. The classifier is used to distinguish upper-body patches from non-upper-body patches and used Histogram of Oriented Gradient (HOG) algorithm for feature selection.}
\end{cvitems}
}

%------------------------------------------------

%\projentry
%{Rating Prediction Based on Yelp Reviews} % Name
%{Python, Matlab} % Skills
%{ % Description(s) of experience/contributions/knowledge
%\begin{cvitems}
%\item{Implemented a {LASSO} regression solver to predict the number of stars a restaurant will receive based on the text reviews, resulting a 91\% accuracy.}
%\end{cvitems}
%}

%------------------------------------------------

\projentry
{Predictive Model for Biological Data Analysis} % Name
{C++} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Developed a LASSO regression solver to predict and improve experimental design. It was integrated into a bioinformatics system that enables the scientist to upload their own data and analyze it in School of Medicine of Stony Brook University.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Load-Balancing Algorithm Developed for Heterogeneous Clusters} % Name
{C, PHP, Httperf, Apache} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Proposed a scalable Load Balancing algorithm for large heterogeneous cluster systems. Performed validation experiments on both Apache based clusters and Amazon EC2 web service.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Routing Allocation Algorithm Developed for CDN Data Centers} % Name
{C, PHP, Httperf, Apache} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Proposed a geographical allocation algorithm for data centers to improve the performance among CDN services. Performed validation experiments on both synthetic data and real web service with Apache based load balancer.}
\end{cvitems}
}

%------------------------------------------------

\projentry
{Social Networking Website Development} % Name
{JDBC, MySQL, HTML, JavaScript} % Skills
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item{Designed a relational database system to support the operations of a social networking website, which contains user-level transactions, user access control and user-friendly interface.}
\end{cvitems}
}

%------------------------------------------------
\end{cventries}